Supplementary material

### 2021-06-29 submission/supplement.rmd
update supplement

### Constant treatment effect
Assuming a constant relative treatment effect, fit the adjusted model in \@ref(eq:risk). Then, an estimate of absolute benefit can be derived from $$\hat{f}_{\text{benefit}}(lp\given \bm{x}, \hat{\bm{\beta}}) = g(lp) - g(lp+\hat{\gamma}) $$

### Linear interaction
The assumption of constant relative treatment effect is relaxed modeling a linear interaction of treatment with the risk linear predictor: 
$$E\{y\given \bm{x}, t_x, \hat{\bm{\beta}}\} = g\big(lp+(\delta_0+\delta_1lp)t_x\big)$$
We predict absolute benefit from $$\hat{f}_{\text{benefit}}(lp\given\bm{x}, \hat{\bm{\beta}}) = g(lp) - g\big(\delta_0+(1+\delta_1)lp\big)$$

### Non-linear interaction
Finally, we drop the linearity assumption and predict absolute benefit by taking the difference between smooth fits, separately derived in each treatment arm:
$$f_{\text{benefit}}(lp\given\bm{x},\hat{\bm{\beta}}) = \hat{f}_{\text{smooth}}(lp\given \bm{x}, \hat{\bm{\beta}}, t_x=0) - \hat{f}_{\text{smooth}}(lp\given \bm{x}, \hat{\bm{\beta}}, t_x=1)$$

>>>>

### Constant treatment effect
Assuming a constant relative treatment effect, fit the adjusted model in
\@ref(eq:risk). Then, an estimate of absolute benefit can be derived from$$\hat{f}_{\text{benefit}}(lp\given \bm{x}, \hat{\bm{\beta}}) = g(lp) - g(lp+\hat{\gamma}) $$

### Linear interaction
The assumption of constant relative treatment effect is relaxed modeling a
linear interaction of treatment with the risk linear predictor:
$$E\{y\given \bm{x}, t_x, \hat{\bm{\beta}}\} = g\big(lp+(\gamma_0+\gamma_1lp)t_x\big)$$
We predict absolute benefit from $$\hat{f}_{\text{benefit}}(lp\given\bm{x}, \hat{\bm{\beta}}) = g(lp) - g\big(\gamma_0+(1+\gamma_1)lp\big)$$

### Restricted cubic splines
Finally, we drop the linearity assumption and predict absolute benefit using smoothing with restricted cubic splines with 3, 4, and 5 knots. More specifically, we fit the model:

$$P(y=1\given lp, t_x) = g\big(\beta_0+\beta_{t_x}t_x+f_{RCS}(lp) + f_{RCS}(lp)\times t_x\big)$$
where
$$f_{RCS}(x)=\alpha_0+\alpha_1h_1(x)+\alpha_2h_2(x)+\dots+\alpha_{k-1}h_{k-1}(x)$$ with
$$h_{j+1}(x)= (x-t_j)^3-(x-t_{k-1})_+\frac{t_k-t_j}{t_k-t_{k-1}}+(x-t_k)^3_+\frac{t_{k-1}-t_j}{t_k-t_{k-   1}}$$
and $t_1,\dots,t_k$ are the selected knots. We predict absolute benefit from $$\hat{f}_{\text{benefit}}(lp \given \bm{x},\hat{\bm{\beta}})=P(y=1\given lp, t_x=0)-P(y=1\given lp,t_x=1)$$.
